%-------------------------
% Resume in Latex
% Author : Suleyman Kiani
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%-----------Header-----------
\begin{center}
    \textbf{\Huge \scshape Suleyman Kiani} \\ \vspace{1pt}
    \small +1 (289) 788-8260 $|$ \href{mailto:kianis4@mcmaster.ca}{\underline{kianis4@mcmaster.ca}} $|$ \href{https://www.linkedin.com/in/suleyman-kiani}{\underline{linkedin.com/in/suleyman-kiani}} $|$ \href{https://github.com/kianis4}{\underline{github.com/kianis4}} $|$ \href{https://suleyman.io}{\underline{suleyman.io}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {McMaster University}{Hamilton, ON}
      {Bachelor of Applied Science (BASc) in Computer Science}{Sept. 2018 - Nov. 2024}
    \resumeSubheading
      {McMaster University}{Hamilton, ON}
      {Master of Engineering (MEng) in Computing and Software}{Sept. 2025 - Present}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Associate Account Manager of Equipment Finance}{Sept. 2025 - Present}
      {Mitsubishi HC Capital Canada}{Burlington, ON}
      \resumeItemListStart
        \resumeItem{Structured and funded equipment deals valued at \textbf{\$500K–\$3M+} using in-depth credit analysis and financial modeling, achieving a \textbf{95\% approval rate} across construction and transportation sectors.}
        \resumeItem{Developed and optimized financial models and amortization schedules with \textbf{TValue}, \textbf{Excel}, and \textbf{Power BI}, enhancing pricing precision by \textbf{15\%} and improving deal profitability visibility.}
        \resumeItem{Streamlined interdepartmental processes by implementing \textbf{Salesforce Lightning} automations, reducing deal turnaround times by \textbf{30\%} and ensuring seamless execution from origination to funding.}
        \resumeItem{Delivered data-driven insights via \textbf{Power BI}, conducting variance analysis that improved portfolio tracking accuracy by \textbf{20\%} and supported strategic growth in multi-million-dollar asset classes.}
      \resumeItemListEnd
    \resumeSubheading
      {Junior Web Developer}{May 2021 - Jun. 2022}
      {Giftcash Inc.}{Remote}
      \resumeItemListStart
        \resumeItem{Migrated a legacy \textbf{Python}/\textbf{Django} monolith to a \textbf{Node.js} \textbf{AWS Lambda} serverless architecture, boosting scalability by \textbf{15\%} and reducing infrastructure costs by \textbf{20\%} through efficient resource allocation.}
        \resumeItem{Optimized \textbf{PostgreSQL} database performance using indexing, caching, and query optimization, cutting response times by \textbf{20\%} and enhancing user experience across web applications.}
        \resumeItem{Automated data extraction workflows with \textbf{Puppeteer} and \textbf{Axios}, streamlining gift card balance verifications and increasing operational efficiency by \textbf{25\%} through reduced manual intervention.}
        \resumeItem{Established \textbf{Jenkins} and \textbf{GitHub Actions} CI/CD pipelines, enabling rapid development cycles and reducing deployment times by \textbf{30\%}, fostering a more agile and responsive development environment.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\href{https://www.solsticepilates.ca/}{\textbf{SKompXcel StudioOS — Solstice Edition}} $|$ \emph{TypeScript, Next.js, AWS}}{Jul. 2025 - Present}
          \resumeItemListStart
            \resumeItem{Engineered a serverless cloud infrastructure on \textbf{AWS}, utilizing \textbf{SES} for email, \textbf{CloudWatch} for monitoring, ensuring \textbf{99.9\% uptime} and seamless scalability for Pilates studio management.}
            \resumeItem{Integrated \textbf{Square API} for payment processing, automating billing and financial reporting, achieving a \textbf{30\% reduction in manual errors} and ensuring PCI compliance.}
            \resumeItem{Developed a responsive frontend with \textbf{React} and \textbf{Tailwind CSS}, leveraging modular components and optimized state management to enhance user experience by \textbf{40\% across all devices}.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\href{https://www.applify-ai.com/}{\textbf{Applify AI - AI-Powered Resume Optimization SAAS}} $|$ \emph{TypeScript, Next.js, OpenAI GPT-4o}}{Feb. 2025 - Present}
          \resumeItemListStart
            \resumeItem{Developed AI-driven resume enhancement using \textbf{OpenAI GPT-4o}, \textbf{boosting relevance by 30\%} through real-time keyword analysis and skill categorization, tailored for ATS and recruiters.}
            \resumeItem{Engineered secure authentication with \textbf{NextAuth.js}, leveraging \textbf{JWT} and \textbf{MongoDB} to ensure robust user data integrity, supporting \textbf{80 paying users within 2 months} of platform launch.}
            \resumeItem{Integrated \textbf{Stripe} for subscription management, enabling premium feature access, \textbf{increasing user engagement by 40\%} and establishing a sustainable monetization strategy.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\href{https://www.skompxcel.com/}{\textbf{SKompXcel Academic Solutions}} $|$ \emph{Next.js, Python, C++}}{Jan. 2024 - Present}
          \resumeItemListStart
            \resumeItem{Engineered a full-stack platform with \textbf{Next.js} and \textbf{Python}, scaling to support 80+ students, achieving \textbf{95\% grade improvement} post four sessions, enhancing personalized tutoring.}
            \resumeItem{Deployed a cloud mentorship system on \textbf{GCP}, optimizing resource allocation, \textbf{reducing server costs by 30\%}, and maintaining 100\% uptime for 1,200+ tutoring hours globally.}
            \resumeItem{Developed a scalable web app using \textbf{Next.js}, enhancing user experience through a streamlined onboarding process, significantly improving user engagement and retention rates.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\href{https://github.com/kianis4/IOS-Workout-Tracker}{\textbf{OverloadPT: Intelligent Fitness Tracking Platform}} $|$ \emph{Swift, SwiftUI, Combine}}{Jul. 2025}
          \resumeItemListStart
            \resumeItem{Developed OverloadPT, an advanced iOS fitness tracking platform using \textbf{Swift} and \textbf{SwiftUI}, integrating \textbf{MVVM} architecture and \textbf{Coordinator pattern} for improved code maintainability and scalability.}
            \resumeItem{Engineered a Progressive Overload Engine with AI-driven machine learning to recommend weight progressions and detect plateaus, significantly optimizing user strength gains.}
            \resumeItem{Optimized app performance using \textbf{SwiftData} and \textbf{Combine}, achieving O(log n) in date filtering algorithms and enhancing responsiveness; also designed a sophisticated workout logging system for precision tracking and real-time performance visualization, increasing user engagement.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\href{https://github.com/kianis4/Mini-Unix-Shell}{\textbf{Custom Unix Shell System}} $|$ \emph{C, GNU Readline, POSIX}}{May 2025}
          \resumeItemListStart
            \resumeItem{Developed a Unix-like shell in \textbf{C} to enhance command-line interface capabilities, supporting interactive command execution with built-in functions.}
            \resumeItem{Implemented core shell functionalities including command parsing, background execution, and I/O redirection, leveraging \textbf{POSIX} system calls for process management.}
            \resumeItem{Designed and integrated a piping mechanism to facilitate inter-process communication, allowing users to connect the output of one command directly to the input of another.}
            \resumeItem{Enhanced user experience by incorporating the \textbf{GNU Readline} library for history navigation and command line editing features.}
            \resumeItem{Engineered custom utilities like 'mystat' using the 'stat()' system call to provide detailed file metadata, improving file management capabilities.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\href{https://suleyman.io/}{\textbf{Personal Full-Stack Portfolio Platform}} $|$ \emph{Next.js, React, Tailwind CSS}}{Oct. 2024 - May 2025}
          \resumeItemListStart
            \resumeItem{Developed a full-stack portfolio platform with \textbf{Next.js} and \textbf{React}, integrating APIs like \textbf{Spotify} and \textbf{Instagram} to enhance user engagement with real-time updates and interactive elements.}
            \resumeItem{Achieved cross-device compatibility and high usability with a mobile-first design utilizing \textbf{Tailwind CSS}, leading to a \textbf{Lighthouse score above 90}.}
            \resumeItem{Implemented a Markdown-based CMS using \textbf{MDX} to optimize article integration and handling, and enhanced site performance with code splitting, lazy loading, and caching techniques for improved load times.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\href{https://github.com/kianis4/Saftey-Net}{\textbf{NYC Crime Analysis System}} $|$ \emph{Java SE 10, OpenCSV, Google Gson}}{Mar. 2023 - Apr. 2025}
          \resumeItemListStart
            \resumeItem{Developed a desktop application to analyze and visualize NYC crime data, featuring a data processing pipeline using \textbf{OpenCSV} to manage four million NYPD records and binary search algorithms to enhance data retrieval.}
            \resumeItem{Enhanced application functionality with geo-specific crime lookup via \textbf{LocationIQ API} and a safest path navigation system employing \textbf{Dijkstra's algorithm} with crime-weighted edges, increasing location-based query accuracy and providing optimal, safe routes.}
            \resumeItem{Ensured software reliability and maintainability through comprehensive unit testing with \textbf{JUnit 4}, achieving high code quality.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\href{https://github.com/kianis4/load-balancer}{\textbf{Scalable Load Balancer System}} $|$ \emph{Python, TCP/IP Sockets, Multi-threading}}{Feb. 2025}
          \resumeItemListStart
            \resumeItem{Developed and implemented a \textbf{Python}-based Load Balancer System with advanced algorithms like Round-Robin and Least Connections, enhancing high availability, fault tolerance, and server utilization through a multi-threaded architecture.}
            \resumeItem{Integrated health monitoring and fault tolerance features to manage server failures dynamically, coupled with the \textbf{\textbf{Python} Logging Module} for meticulous tracking of request flows, server status, and response times, bolstering system throughput and continuous service.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\href{https://github.com/kianis4/-neural-networks-zero-to-hero.}{\textbf{Micrograd Neural Network Framework}} $|$ \emph{Python, Jupyter Notebook, Micrograd}}{Jan. 2025}
          \resumeItemListStart
            \resumeItem{Developed and optimized the Micrograd Neural Network Framework by implementing `Value`, `Neuron`, `Layer`, and `MLP` components, facilitating automatic differentiation and backpropagation, and enhancing user comprehension of machine learning fundamentals.}
            \resumeItem{Utilized \textbf{Jupyter Notebooks} for interactive demonstrations, enabling users to visualize computational graphs and experiment with concepts such as forward pass and gradient descent, thus simplifying complex topics like gradient evaluation and parameter optimization.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming languages}{: TypeScript, Swift, C, JavaScript, Java, Python, PHP} \\
     \textbf{Frameworks}{: Next.js, React, Tailwind CSS, SwiftUI, Combine, Prisma, PyTorch, Django, Express} \\
     \textbf{Databases}{: PostgreSQL, MongoDB, SwiftData, S3, DynamoDB} \\
     \textbf{Cloud services \& Tools}{: AWS, Vercel, GCP, Docker, GitHub Actions, Jenkins}
    }}
\end{itemize}


\end{document}